### 2024-02-06 README.Rmd
remove data-building section from readme

# ### UK data
# 
# library(parlitools)
# 
# # prepare the data
# # extract and join census and election data from parlitools package
# census_11 <- parlitools::census_11 |> 
#   select(-constituency_name,-constituency_type,-pano, -region, -country)
# bes_2019 <- parlitools::bes_2019
# 
# elect_results <- left_join(bes_2019,census_11, by=c("ons_const_id"))
# 
# # download constituency boundaries for 2019 using the st_read() command below
# # they come from: https://geoportal.statistics.gov.uk/datasets/ons::wpc-dec-2019-ultra-generalised-clipped-boundaries-uk
# # which results in file: WPC_Dec_2019_UGCB_UK_2022_-5406762260244410508.geojson
# 
# uk_map_download <- st_read(
#   "https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/WPC_Dec_2019_UGCB_UK_2022/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson",
#   quiet = TRUE)
# 
# # only need the boundaries and the IDs for merging with parlitools data
# uk<- uk_map_download |> 
#   select(pcon19cd,geometry) |> 
#   st_transform(crs=27700) |> 
#   st_make_valid() # ensure valid line overlaps etc
# 
# # create dataframe for filtering-out speaker constituencies below
# speakers <- data.frame(
#   year = c(2017,2019),
#   constituency_name = c("Buckingham","Chorley")
# )
# 
# # join constituency polygons to parlitools data
# # filter out Scotland and Northern Ireland
# # filter out the speakers' constituencies
# # calculate the desired explanatory variables
# # make levels into factors for use with `mgcv`
# 
# df <- elect_results |> 
#   left_join(uk, by=c("ons_const_id"="pcon19cd")) |> 
#   # filter(!country %in% c("Scotland","Northern Ireland")) |> 
#   filter(!country %in% c("Northern Ireland")) |> 
#   # filter(!constituency_name %in% speakers$constituency_name) |>
#   mutate(degree_educated = qual_level_4,
#          health_not_good = health_fair + health_bad + health_very_bad,
#          white = ethnicity_white,
#          con_change = con_19 - con_17, # difference in %
#          lab_change = lab_19 - lab_17,
#          con_swing = (con_change - lab_change)/2, # Butler swing
#          region = factor(ifelse(county == "Merseyside", "Merseyside", region)),
#          county = factor(county)) |> 
#   st_as_sf()
# 
# # give the empty speaker seats the mean value, just for demostration purposes here
# df$con_swing[df$constituency_name %in% speakers$constituency_name] <- mean(df$con_swing,na.rm = TRUE)
# 
# # create region boundaries layer for mapping
# regions <- df |> group_by(region) |> 
#   summarise() |> 
#   st_as_sf() |> 
#   st_transform(crs=27700)
# 
# # create county boundaries layer for mapping
# counties <- df |> group_by(county) |> 
#   summarise() |> 
#   st_as_sf() |> 
#   st_transform(crs=27700)
# 
# # create outline layer for mapping
# uk_outline <- df |> 
#   summarise() |> 
#   st_as_sf() |> 
#   st_transform(crs=27700)
# 
# # filter out required independent variables and scale them
# # then add back to the features which were not scaled
# df_scaled <- df |> 
#   st_drop_geometry() |> 
#   select(degree_educated,
#          health_not_good,
#          white) |> 
#   scale() |> 
#   as.data.frame() |> 
#   mutate(con_swing = df$con_swing,
#          population = df$population,
#          region = factor(df$region),
#          county = factor(df$county),
#          constituency_name = df$constituency_name)
# 
# # create a simple features (spatial) version of this with a geometry column
# df_scaled_sf <- df_scaled |> 
#   mutate(geometry = df$geometry) |> 
#   st_as_sf() |> 
#   st_transform(crs=27700)

# df_scaled_sf <- uk_election
```

@@

```{r}
st_bridges(df = uk_election|> filter(region %in% c("Wales","South West")),
           geom_col_name = "constituency_name",
           link_islands_k = 2)  |> 
  st_manual_join_nb("Gower","St Ives")
```

>>>>

@@

```{r}
st_bridges(df = uk_election|> filter(region %in% c("Wales","South West")),
           geom_col_name = "constituency_name",
           link_islands_k = 2)  |> 
  st_manual_join_nb("Gower","St Ives") |> 
  st_quickmap_nb()
```
